---
title: "Lab 4 Package Examples"
author: "David G Norvell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab 4 Package Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library("Lab4Package")
```

Function 1: Print ASCII

Description: Reads a Text File and prints to Console, intended for ASCII art but can read any text.

Usage: read a .txt file into an object (file <- system.file(...txt)) or place file directly in the working directory and pass in the filename

```{r}
print_ascii(system.file("extdata", "light_ascii.txt", package = "Lab4Package"))
```

Output: Whatever file contents were present, printed to the terminal

Function 2: Birthday Function!

Description: Calculates the probability that at least two people in a group of n share the same birthday, assuming 365 days in a year. Returns a numeric vector of probabilities for each n.

Usage: Input an integer to represent the number of people in the sample

```{r}
birthdayDGN(30)
```

Output: The probability of 2 people sharing the same birthday

Function 3: Hypergeometric Simulation

Description: Simulates the hypergeometric distribution by repeated sampling. N is the population size, r is the number of successes in the population, and n is the sample size. Returns a barplot of the proportion of successes and the frequency table.

Usage: Run with Default Values for an Example, or pass in args (iter=??,N =?? ,r=??,n =??) all are integer type

```{r}
myhyper()
```

Output: Barplot showing the proportions of successes in the simulated trials

Function 4: Normal Curve Shader

Description: Plots a normal distribution curve with mean $\mu$ and standard deviation $\sigma$ Shades the area from $-\infty$ to a and calculates $P(X \leq a)$

Usage: Set $\mu$ , $\sigma$ and a. All integer types.

```{r}
myncurve(mu=10,sigma=2,a=20)
```

Output: The cumulative probability up to a, represented by the shaded area

Dataset: FIRE

Description: A Dataset from the the book https://www.crcpress.com/Statistics-for-Engineering-and-the-Sciences/Mendenhall-Sincich/p/book/9781498728850
With 2 columns DISTANCE (cm) and DAMAGE (dollars)

```{r}
head(Lab4Package::fire)
```
